---
title: "mailing_parse"
author: "anastasia molotova"
date: "4/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, error = FALSE)
```

# Loading the data (2018-2020)

```{r}
data_apr <- read.delim("data/mails/2018/2018-April.txt", header = FALSE, col.names = "text") 
data_aug <- read.delim("data/mails/2018/2018-August.txt", header = FALSE, col.names = "text")
data_dec <- read.delim("data/mails/2018/2018-December.txt", header = FALSE, col.names = "text")
data_feb <- read.delim("data/mails/2018/2018-February.txt", header = FALSE, col.names = "text")
data_jan <- read.delim("data/mails/2018/2018-January.txt", header = FALSE, col.names = "text")
data_jul <- read.delim("data/mails/2018/2018-July.txt", header = FALSE, col.names = "text")
data_jun <- read.delim("data/mails/2018/2018-June.txt", header = FALSE, col.names = "text")
data_mar <- read.delim("data/mails/2018/2018-March.txt", header = FALSE, col.names = "text")
data_may <- read.delim("data/mails/2018/2018-May.txt", header = FALSE, col.names = "text")
data_nov <- read.delim("data/mails/2018/2018-November.txt", header = FALSE, col.names = "text")
data_oct <- read.delim("data/mails/2018/2018-October.txt", header = FALSE, col.names = "text")
data_sep <- read.delim("data/mails/2018/2018-September.txt", header = FALSE, col.names = "text")

data_2018 = rbind(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

print(dim(data_2018)[1] == (dim(data_apr)[1] + dim(data_aug)[1] + dim(data_dec)[1] + dim(data_feb)[1] + dim(data_jan)[1] + dim(data_jul)[1] + dim(data_jun)[1] + dim(data_mar)[1] + dim(data_may)[1] + dim(data_nov)[1] + dim(data_oct)[1] + dim(data_sep)[1]))

rm(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

```

```{r}
data_apr <- read.delim("data/mails/2019/2019-April.txt", header = FALSE, col.names = "text") 
data_aug <- read.delim("data/mails/2019/2019-August.txt", header = FALSE, col.names = "text")
data_dec <- read.delim("data/mails/2019/2019-December.txt", header = FALSE, col.names = "text")
data_feb <- read.delim("data/mails/2019/2019-February.txt", header = FALSE, col.names = "text")
data_jan <- read.delim("data/mails/2019/2019-January.txt", header = FALSE, col.names = "text")
data_jul <- read.delim("data/mails/2019/2019-July.txt", header = FALSE, col.names = "text")
data_jun <- read.delim("data/mails/2019/2019-June.txt", header = FALSE, col.names = "text")
data_mar <- read.delim("data/mails/2019/2019-March.txt", header = FALSE, col.names = "text")
data_may <- read.delim("data/mails/2019/2019-May.txt", header = FALSE, col.names = "text")
data_nov <- read.delim("data/mails/2019/2019-November.txt", header = FALSE, col.names = "text")
data_oct <- read.delim("data/mails/2019/2019-October.txt", header = FALSE, col.names = "text")
data_sep <- read.delim("data/mails/2019/2019-September.txt", header = FALSE, col.names = "text")

data_2019 = rbind(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

print(dim(data_2019)[1] == (dim(data_apr)[1] + dim(data_aug)[1] + dim(data_dec)[1] + dim(data_feb)[1] + dim(data_jan)[1] + dim(data_jul)[1] + dim(data_jun)[1] + dim(data_mar)[1] + dim(data_may)[1] + dim(data_nov)[1] + dim(data_oct)[1] + dim(data_sep)[1])) 

rm(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

```



```{r}
data_apr <- read.delim("data/mails/2020/2020-April.txt", header = FALSE, col.names = "text")
data_aug <- read.delim("data/mails/2020/2020-August.txt", header = FALSE, col.names = "text")
data_dec <- read.delim("data/mails/2020/2020-December.txt", header = FALSE, col.names = "text")
data_feb <- read.delim("data/mails/2020/2020-February.txt", header = FALSE, col.names = "text")
data_jan <- read.delim("data/mails/2020/2020-January.txt", header = FALSE, col.names = "text")
data_jul <- read.delim("data/mails/2020/2020-July.txt", header = FALSE, col.names = "text")
data_jun <- read.delim("data/mails/2020/2020-June.txt", header = FALSE, col.names = "text")
data_mar <- read.delim("data/mails/2020/2020-March.txt", header = FALSE, col.names = "text")
data_may <- read.delim("data/mails/2020/2020-May.txt", header = FALSE, col.names = "text")
data_nov <- read.delim("data/mails/2020/2020-November.txt", header = FALSE, col.names = "text")
data_oct <- read.delim("data/mails/2020/2020-October.txt", header = FALSE, col.names = "text")
data_sep <- read.delim("data/mails/2020/2020-September.txt", header = FALSE, col.names = "text")

data_2020 = rbind(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

print(dim(data_2020)[1] == (dim(data_apr)[1] + dim(data_aug)[1] + dim(data_dec)[1] + dim(data_feb)[1] + dim(data_jan)[1] + dim(data_jul)[1] + dim(data_jun)[1] + dim(data_mar)[1] + dim(data_may)[1] + dim(data_nov)[1] + dim(data_oct)[1] + dim(data_sep)[1])) 

rm(data_apr, data_aug, data_dec, data_feb, data_jan, data_jul, data_jun, data_mar, data_may, data_nov, data_oct, data_sep)

```

```{r}
my_data = rbind(data_2018, data_2019, data_2020)
rm(data_2018, data_2019, data_2020)
```

# Counting threads

```{r}
library(stringr)
my_data$thread_count = substring(my_data$text, 1, 20)
my_data$thread_count = str_count(my_data$thread_count, ">")
summary(my_data$thread_count)
```

# Detecting the subjects, dates, message_ids and replies (binary)

```{r}
library(tidyverse)
my_data$from = ifelse(str_detect(substring(my_data$text, 1, 20), "From "), 1, 0)
my_data$author = ifelse(str_detect(substring(my_data$text, 1, 20), "From:"), 1, 0)
my_data$date = ifelse(str_detect(substring(my_data$text, 1, 20), "Date:"), 1, 0)
my_data$subject = ifelse(str_detect(substring(my_data$text, 1, 20), "Subject:"), 1, 0)
my_data$message_id = ifelse(str_detect(substring(my_data$text, 1, 20), "Message-ID:"), 1, 0)
my_data$in_reply_to = ifelse(str_detect(substring(my_data$text, 1, 20), "In-Reply-To:"), 1, 0)

```

# Creating a unique id for each message

```{r}
my_data$info = ifelse(my_data$from == 1, paste0("start_",  seq(from = 1, to = 830846) ), NA)

library(zoo)
my_data$info = na.locf(my_data$info)
```

# Detecting the text(body) of the messages

```{r}
my_data$message_text = ifelse(my_data$message_id == 1, "start",
                              ifelse(my_data$from == 1, "end", NA))

my_data = my_data %>% 
 group_by(grp = cumsum(!is.na(message_text))) %>% 
 mutate(message_text = replace(message_text, first(message_text) == 'start', 'text')) %>% 
 ungroup() %>% 
 select(-grp)
```

# Detecting the author's e-mails and names

```{r}
my_data$author_mail = ifelse(my_data$author == 1, str_replace(my_data$text, "From:", ""), 0)
my_data$author_mail = str_replace(my_data$author_mail, "@ending from", "")
my_data$author_mail = str_replace(my_data$author_mail, "@end|ng |rom", "")

my_data$author_name = str_extract(my_data$author_mail, pattern = "(?<=\\().*(?=\\))")
my_data$author_mail = str_replace_all(my_data$author_mail, pattern = "(?<=\\().*(?=\\))", "")
my_data$author_mail = gsub("\\(|\\)", "", my_data$author_mail)
```

# Detecting dates

```{r}
library(lubridate)
my_data$date = ifelse(my_data$date == 1, str_replace(my_data$text, "Date:", ""), 0)

my_data$date = gsub("\\+.*","", my_data$date)
my_data$date = gsub("\\-.*","", my_data$date) 
```

# Detecting the subject

```{r}
my_data$subject = ifelse(my_data$subject == 1, str_replace(my_data$text, "Subject:", ""), 0)
```

# Detecting message_id

```{r}
my_data$message_id = ifelse(my_data$message_id == 1, str_replace(my_data$text, "Message-ID:", ""), 0)
my_data$message_id = str_replace(my_data$message_id, "<", "")
my_data$message_id = str_replace(my_data$message_id, ">", "")
```

# Getting the "in-reply-to" column

```{r}
my_data$in_reply_to = ifelse(my_data$in_reply_to == 1, str_replace(my_data$text, "In-Reply-To:", ""), 0)
#убрать < и >
my_data$in_reply_to = str_replace(my_data$in_reply_to, "<", "")
my_data$in_reply_to = str_replace(my_data$in_reply_to, ">", "")
```

# Getting the text

```{r}
my_data$message_text = ifelse(my_data$message_text == 'text', my_data$text, NA)
my_data$message_text = ifelse(str_detect(my_data$message_text, "Message-ID:"), NA, my_data$message_text)
```

# Deleting blank spaces

```{r}
my_data = my_data[!(is.na(my_data$text) | my_data$text == ""), ]
```

# Cleaning the table

```{r}
my_data = my_data %>% 
        select(-from, -author)

my_data$date = ifelse(my_data$date == 0, NA, my_data$date)
my_data$subject = ifelse(my_data$subject == 0, NA, my_data$subject)
my_data$message_id = ifelse(my_data$message_id == 0, NA, my_data$message_id)
my_data$author_mail = ifelse(my_data$author_mail == 0, NA, my_data$author_mail)
my_data$author_name = ifelse(my_data$author_name == 0, NA, my_data$author_name)
my_data$in_reply_to = ifelse(my_data$in_reply_to == 0, NA, my_data$in_reply_to)
```

# Deleting repeated rows

```{r}
my_data = my_data %>% distinct() 
```

# Tidy format

```{r}
my_data = my_data %>% 
  group_by(info) %>% 
  fill(author_mail, author_name, date, subject, message_id, in_reply_to) %>% 
  fill(author_mail, author_name, date, subject, message_id, in_reply_to, .direction = "up") 
```

# Text cleaning

```{r}
my_data$message_text = tolower(my_data$message_text)

my_data$message_text <- gsub("@\\w+", "", my_data$message_text)
my_data$message_text <- gsub("https?://.+", "", my_data$message_text)
my_data$message_text <- gsub("\\d+\\w*\\d*", "", my_data$message_text)
my_data$message_text <- gsub("#\\w+", "", my_data$message_text)
my_data$message_text <- gsub("[^\x01-\x7F]", "", my_data$message_text)
my_data$message_text <- gsub("[[:punct:]]", " ", my_data$message_text)

my_data$message_text <- gsub("\n", " ", my_data$message_text)
my_data$message_text <- gsub("^\\s+", "", my_data$message_text)
my_data$message_text <- gsub("\\s+$", "", my_data$message_text)
my_data$message_text <- gsub("[ |\t]+", " ", my_data$message_text)
```

# Detecting either it is a question or an answer

```{r}
my_data$quest_or_answ_bin = ifelse(str_detect(substring(my_data$text, 1, 20), "In-Reply-To:"), "a", ifelse(str_detect(substring(my_data$text, 1, 20), "References:"), "a", NA))

my_data = my_data %>% 
  group_by(info) %>% 
  fill(quest_or_answ_bin) %>% 
  fill(quest_or_answ_bin, .direction = "up") 

my_data$quest_or_answ_bin = ifelse(is.na(my_data$quest_or_answ_bin), "q", "a")
```

# Preprocess the dates

```{r}
my_data$date = str_trim(my_data$date)
# checking the exact patternal format
my_data$date = str_extract_all(my_data$date, "(Mon|Tue|Wed|Thu|Fri|Sat|Sun|Monday|Tuesday|Wednesday|Thursday|Friday|Saturday|Sunday).\\s([0-9]|[0-3][0-9])\\s(Jan|Feb|Mar|Apr|May|Jun|Jul|Aug|Sep|Oct|Nov|Dec)\\s(2018|2019|2020)\\s([0|1|2][0|1|2|3|4|5|6|7|8|9]):([0-9]{2}):([0-9]{2})", simplify = TRUE)
```

# Link-sharing

```{r}
data1 = my_data %>% select(info, text, thread_count) %>% filter(thread_count == 0) %>% select(-thread_count)
data1$url_bin = ifelse(str_detect(data1$text, "https?://.+"), 1, NA)
summary(data1$url_bin)

my_data = full_join(my_data, data1)

my_data = my_data %>% 
  group_by(info) %>% 
  fill(url_bin) %>% 
  fill(url_bin, .direction = "up")
my_data$url_bin = ifelse(is.na(my_data$url_bin), 0, my_data$url_bin)
table(my_data$url_bin)
rm(data1)
```

# Few more preprocessing

```{r}
my_data = my_data %>% select(-text) %>% filter(thread_count == 0) %>% select(-thread_count)

#load("~/diploma/data/mails/ml_cleaned.RData")
#library(tidyverse)
```

Divide the data into meta and texts (body)

```{r}
#my_data$drop = ifelse(str_detect(substring(my_data$text, 1, 20), ">"), 1, 0)
#my_data = my_data %>% filter(drop == 0) %>% select(-drop)

texts = my_data %>% select(info, message_text) %>% filter(!is.na(message_text))
texts = texts[!(is.na(texts$message_text) | texts$message_text == ""), ]

meta = my_data %>% select(-message_text)
meta = meta %>% distinct() 
meta = meta %>% select(-subject, -author_mail)

meta = meta %>% distinct()

rm(my_data)

```

How many unique mails & authors are there?

```{r}
print(c(length(unique(meta$info)), "unique e-mails"))
print(c(length(unique(meta$author_name)), "unique authors"))
```

Datetime formatting

```{r}
library(lubridate)

#meta$date1 = str_replace(meta$date, "(Mon|Tue|Wed|Thu|Fri|Sat|Sun|Monday|Tuesday|Wednesday|Thursday|Friday|Saturday|Sunday).", "")
#meta$date1 = str_remove_all(meta$date1, ">")

meta$date = str_replace(meta$date, "(Mon|Tue|Wed|Thu|Fri|Sat|Sun|Monday|Tuesday|Wednesday|Thursday|Friday|Saturday|Sunday).", "")

meta = meta[!(is.na(meta$date) | meta$date == ""), ]
meta$date = dmy_hms(meta$date)

meta = meta %>% filter(date >= "2018-01-01 00:00:00" & date <= "2020-12-31 23:59:59" )

```

Dealing with texts

```{r}
texts <- texts %>% mutate(ind = row_number())
texts <- texts %>% group_by(info) %>% mutate(ind = row_number()) %>%
  tidyr::spread(key = ind, value = message_text)
texts [is.na(texts)] <- ""
texts <- tidyr::unite(texts, text,-info,sep =" " )
texts$text <- trimws(texts$text)
```

Creating the final dataframe 

```{r}
all = full_join(meta, texts)
```

# Saving the cleaned data

```{r}
#rdata
save(all, file = "data/mails/mailing_lists.RData")

#load("data/mails/mailing_lists.RData")

#csv
write.csv(all,'data/mails/mailing_lists.csv', row.names = FALSE, fileEncoding = "UTF-8")
```
